STAT 253 Final Project

### 2022-10-16 Final_Project_Work_HW2.Rmd
HW3 edits

```{r}
library(ISLR)
library(dplyr)
library(readr)
library(broom)
library(ggplot2)
library(tidymodels) 
library(stringr)
library(splitstackshape)
tidymodels_prefer()
```

@@

@@

best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
```

@@

@@

@@

@@

# data_cv10 <- imdb_clean %>% 
#     filter(No_of_Votes < 1500000 & IMDB_Rating < 9) %>% # remove outliers
#     vfold_cv(v = 10)

data_cv10 <- vfold_cv(imdb_clean, v = 10)

full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    step_rm(Series_Title, Released_Year, Overview,
            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross)

spline_rec <- full_rec %>%
     step_ns(Runtime, deg_free = 2) %>% 
    step_ns(Meta_score, deg_free = 2) %>%
     step_ns(No_of_Votes, deg_free = 6)

movie_wf <- workflow() %>%
    add_model(lm_spec) %>%
    add_recipe(full_rec)

@@

fit_resamples(
    movie_wf,
    resamples = data_cv10, # cv folds
    metrics = metric_set(mae,rmse,rsq)                     
) %>% collect_metrics()

# This code chunk has an error, but I'm not sure why

# fit_resamples(
#     spline_wf,
#     resamples = data_cv10, # cv folds
#     metrics = metric_set(mae,rmse,rsq)                     
# ) %>% collect_metrics()
```

@@

# Workflow (Recipe + Model)
lasso_wf_tune <- workflow() %>% 
  add_recipe(data_rec) %>%
  add_model(gam_lasso_spec_tune)

@@

@@

best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse
```

@@

@@

@@

@@

@@

>>>>

```{r}
library(ISLR)
library(dplyr)
library(readr)
library(broom)
library(ggplot2)
library(tidymodels) 
library(stringr)
library(splitstackshape)
library(tidymodels)
library(lubridate)
library(rpart.plot)
library(cluster)
library(forcats)
tidymodels_prefer()
```

@@

full_modelcv <- fit_resamples(full_lm_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))

@@

# Summarize Model Evaluation Metrics (CV)
lasso_mod <- collect_metrics(tune_res) %>%
  filter(.metric == 'rmse') %>% # or choose mae
  select(penalty, rmse = mean)

best_penalty <- select_best(tune_res, metric = 'rmse') # choose penalty value based on lowest mae or rmse

lasso_mod
```

@@

lasso_fit <- fit_resamples(final_wf, resamples = data_cv10, metrics = metric_set(rmse, rsq, mae))

@@

```{r}
gam_mod %>% pluck('fit') %>% summary() 
```

@@

```{r}
spline_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    step_rm(Series_Title, Released_Year, Overview,
            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross) %>%
    step_ns(Runtime, deg_free = 2) %>%
    step_ns(No_of_Votes, deg_free = 6)

spline_rec %>% prep(imdb_clean) %>% juice()
```

@@

@@

cv_output <- fit_resamples( 
  spline_wf, # workflow
  resamples = data_cv10, # cv folds
  metrics = metric_set(mae,rmse,rsq)
)

cv_output %>% collect_metrics()

```{r}
new_mod <- spline_wf %>%
  fit(data = imdb_clean)

new_mod %>%
  tidy()

new_mod %>% 
  tidy() %>% 
  arrange(desc(abs(statistic)))

new_modcv <- fit_resamples(spline_wf, resamples = data_cv10, metrics = metric_set(mae, rmse, rsq))
```

@@

# Workflow (Recipe + Model)
lasso_wf_tune1 <- workflow() %>% 
  add_recipe(data_rec) %>%
  add_model(gam_lasso_spec_tune)

@@

tune_res1 <- tune_grid( # new function for tuning parameters
  lasso_wf_tune1, # workflow
  resamples = data_cv10, # cv folds
  metrics = metric_set(rmse, mae),
  grid = penalty_grid # penalty grid defined above
)

# Visualize Model Evaluation Metrics from Tuning
autoplot(tune_res1) + theme_classic()
```

@@

best_penalty1 <- select_best(tune_res1, metric = 'rmse') # choose penalty value based on lowest mae or rmse
```

@@

# Fit Final Model
final_wf1 <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow

final_fit1 <- fit(final_wf1, data = imdb_clean)

tidy(final_fit1)
```

@@

final_fit1 %>% tidy() %>% filter(estimate != 0)
```

@@

# Visualize Residuals
lasso_mod_out1 <- new_mod %>%
    predict(new_data = imdb_clean) %>%
    bind_cols(imdb_clean) %>%
    mutate(resid = Gross - .pred)

ggplot(lasso_mod_out1, aes(x = .pred, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") + 
    theme_classic()

ggplot(lasso_mod_out1, aes(x = Runtime, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") + 
    theme_classic()

ggplot(lasso_mod_out1, aes(x = IMDB_Rating, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") + 
    theme_classic()

ggplot(lasso_mod_out1, aes(x = No_of_Votes, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") + 
    theme_classic()
```

@@

```{r}
full_modelcv %>% collect_metrics() #OLS
```

```{r}
lasso_fit %>% collect_metrics() #LASSO
```

```{r}
new_modcv %>% collect_metrics() #GAM
```

@@

We want a combination of both, our spline model has the lowest RMSE but could be difficult to interpret. We need more visualization and analysis before we move forward. However we are confident in moving forward.

# Societal Impact

Being that the data here is about movies, the harm that could come from our analysis would be minimal. 
Representation of different races, genders, abilities, etc. is an issue in Hollywood/the greater film industry, and it's likely that the harm our model/analysis produces is already in line with the issues that created and maintain this.
This is because the data we have is on past movies that have come out of this system. This means that whatever has made a movie successful, whether it's due to certain actors or directors, or whatever — this is a standard that has already existed. If we see the movies that have done really well because the cast is predominantly white, well this has been going on a for a long time because Hollywood is racist. Our model can't account for that, but we are aware of it.
